Paper notes

### 2019-08-19 paper_notes.Rmd
ok 3d

library(knitr)
library(Hmisc)
library(ggplot2)
library(gridExtra)
library(ggpubr)
# library(kableExtra)
library(dplyr)
library(grid)
library(ggrepel)
# Here functions that are used.

@@

prob <- function(d_u_e,d_u_v,e_w,par_v){round(1 / (1 + exp(-(e_w*10)*(d_u_e) + (-(v_w*10)*(d_u_v)))),digits= 2)}

@@

@@

e_w <- 0.4
v_w <- 1-e_w

@@

dis_0   <- prob(d_u_e,0.0,e_w,v_w)
dis_0.1 <- prob(d_u_e,0.1,e_w,v_w)
dis_0.2 <- prob(d_u_e,0.2,e_w,v_w)
dis_0.3 <- prob(d_u_e,0.3,e_w,v_w)
dis_0.4 <- prob(d_u_e,0.4,e_w,v_w)
dis_0.5 <- prob(d_u_e,0.5,e_w,v_w)
dis_0.6 <- prob(d_u_e,0.6,e_w,v_w)
dis_0.7 <- prob(d_u_e,0.7,e_w,v_w)
dis_0.8 <- prob(d_u_e,0.8,e_w,v_w)
dis_0.9 <- prob(d_u_e,0.9,e_w,v_w)
dis_1   <- prob(d_u_e,1.0,e_w,v_w)
dis_0.1neg <- prob(d_u_e,-0.1,e_w,v_w)
dis_0.2neg <- prob(d_u_e,-0.2,e_w,v_w)
dis_0.3neg <- prob(d_u_e,-0.3,e_w,v_w)
dis_0.4neg <- prob(d_u_e,-0.4,e_w,v_w)
dis_0.5neg <- prob(d_u_e,-0.5,e_w,v_w)
dis_0.6neg <- prob(d_u_e,-0.6,e_w,v_w)
dis_0.7neg <- prob(d_u_e,-0.7,e_w,v_w)
dis_0.8neg <- prob(d_u_e,-0.8,e_w,v_w)
dis_0.9neg <- prob(d_u_e,-0.9,e_w,v_w)
dis_1neg   <- prob(d_u_e,-1.0,e_w,v_w)

>>>>

library(knitr)
library(Hmisc)
library(ggplot2)
library(gridExtra)
library(ggpubr)
# library(kableExtra)
library(dplyr)
library(grid)
library(ggrepel)
library(magicfor)
library(dplyr)
library(plot3D)
library(rgl)
library(plotly)

# Here functions that are used.

@@

prob <- function(d_u_e,d_u_v,e_w,v_w){round(1 / (1 + exp(-(e_w*k)*(d_u_e) + (-(v_w*k)*(d_u_v)))),digits= 2)}

@@

```{r heatmap-log,  fig.width=5,fig.height=4,fig.cap="Probability to choose alternative location",fig.align="center", include=TRUE, echo=FALSE}

magic_for(print,silent = TRUE)

for (i in seq (-1.0,1.0, by = 0.1)){
  eth_diff <- rep(i,21)
  print(eth_diff)
}

d_u_e <-  magic_result_as_vector()
d_u_v <- rep(seq(-1,1,by = 0.1),21) 
e_w <- 0
v_w <- 1-e_w
k <- 10

df <- data.frame(d_u_e,d_u_v,e_w,v_w)

title_cond_fin <- paste0("Ethnic weight = ",e_w*k,"; ","Value weight = ",v_w*k)
ass <- mutate(df, prap = prob(d_u_e, d_u_v,e_w,v_w))
fina_rast <- ggplot(ass,aes(d_u_e,d_u_v))

 plot_fina_rast <-  suppressWarnings(suppressMessages(
    fina_rast + geom_raster(aes(fill = prap)) + theme_bw() + labs(x = "Diff. ethnic (alternative - current)",y = "Diff. value (alternative - current)") + labs(title = title_cond_fin, caption = "-1: Min Utility Alternative; 1: Max Utility Alternative") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust=0.5),plot.caption = element_text(hjust=0.5)) 
    + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0, colour = "red", linetype = "dotted") + scale_fill_continuous(name = "Probability")
  ))

 fx <- d_u_e
 fy <- d_u_v
 fz <- ass$prap

 # persp(x = seq(-1, 1, by = 0.1),
   #   y = seq(-1, 1, by = 0.1),
   #   fz)

  d <- plot3d(fx,fy,fz,col="blue")
  rgl.postscript("d.eps",fmt="eps")

 test_trida <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", mode="markers", color=fz) %>% layout(legend = list(x = 0.1, y = 0.9))
 #p <- export(p = last_plot(),file = "plotly.png", selenium = NULL)
 #fx

# test_trid <- plot3d(df_3$a,df_3$b,df_3$C)

# plotly_IMAGE(test_trida, width = 500, height = 500, format = "png", scale = 2, out_file = "test.png")

#is.data.frame(ass)
#  print(plot_fina_rast)

print(plot_fina_rast)

# knitr::include_graphics("gg.png" )

# plot3d(fx,fy,fz, col = "blue",xlab = "eth",ylab="val",zlab="prob", type = "s",size = 2)

```{r heat2,  fig.width=5,fig.height=4,fig.cap="Probability to choose alternative location",fig.align="center", include=TRUE, echo=FALSE}

magic_for(print,silent = TRUE)

for (i in seq (-1.0,1.0, by = 0.1)){
  eth_diff <- rep(i,21)
  print(eth_diff)
}

d_u_e <-  magic_result_as_vector()
d_u_v <- rep(seq(-1,1,by = 0.1),21) 
e_w <- 0
v_w <- 1-e_w
k <- 10

df <- data.frame(d_u_e,d_u_v,e_w,v_w)

title_cond_fin <- paste0("Ethnic weight = ",e_w*k,"; ","Value weight = ",v_w*k)
ass <- mutate(df, prap = prob(d_u_e, d_u_v,e_w,v_w))
fina_rast <- ggplot(ass,aes(d_u_e,d_u_v))

 plot_fina_rast <-  suppressWarnings(suppressMessages(
    fina_rast + geom_raster(aes(fill = prap)) + theme_bw() + labs(x = "Diff. ethnic (alternative - current)",y = "Diff. value (alternative - current)") + labs(title = title_cond_fin, caption = "-1: Min Utility Alternative; 1: Max Utility Alternative") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust=0.5),plot.caption = element_text(hjust=0.5)) 
    + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0, colour = "red", linetype = "dotted") + scale_fill_continuous(name = "Probability")
  ))

 fx <- d_u_e
 fy <- d_u_v
 fz <- ass$prap

 # persp(x = seq(-1, 1, by = 0.1),
   #   y = seq(-1, 1, by = 0.1),
   #   fz)

#  d <- plot3d(fx,fy,fz,col="blue")
#  rgl.postscript("d.eps",fmt="eps")

 test_trida <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", mode="markers", color=fz) 
 #p <- export(p = last_plot(),file = "plotly.png", selenium = NULL)
 #fx

# test_trid <- plot3d(df_3$a,df_3$b,df_3$C)

# plotly_IMAGE(test_trida, width = 500, height = 500, format = "png", scale = 2, out_file = "test.png")

#is.data.frame(ass)
#  print(plot_fina_rast)

print(test_trida)
print(plot_fina_rast)

# knitr::include_graphics("gg.png" )

# plot3d(fx,fy,fz, col = "blue",xlab = "eth",ylab="val",zlab="prob", type = "s",size = 2)

@@

e_w <- 0.6
v_w <- 1 - e_w
k <- 10

@@

dis_1neg   <- prob(d_u_e,-1.0,e_w,v_w)
dis_0.9neg <- prob(d_u_e,-0.9,e_w,v_w)
dis_0.8neg <- prob(d_u_e,-0.8,e_w,v_w)
dis_0.7neg <- prob(d_u_e,-0.7,e_w,v_w)
dis_0.6neg <- prob(d_u_e,-0.6,e_w,v_w)
dis_0.5neg <- prob(d_u_e,-0.5,e_w,v_w)
dis_0.4neg <- prob(d_u_e,-0.4,e_w,v_w)
dis_0.3neg <- prob(d_u_e,-0.3,e_w,v_w)
dis_0.2neg <- prob(d_u_e,-0.2,e_w,v_w)
dis_0.1neg <- prob(d_u_e,-0.1,e_w,v_w)
dis_0   <- prob(d_u_e,0.0,e_w,v_w)
dis_0.1 <- prob(d_u_e,0.1,e_w,v_w)
dis_0.2 <- prob(d_u_e,0.2,e_w,v_w)
dis_0.3 <- prob(d_u_e,0.3,e_w,v_w)
dis_0.4 <- prob(d_u_e,0.4,e_w,v_w)
dis_0.5 <- prob(d_u_e,0.5,e_w,v_w)
dis_0.6 <- prob(d_u_e,0.6,e_w,v_w)
dis_0.7 <- prob(d_u_e,0.7,e_w,v_w)
dis_0.8 <- prob(d_u_e,0.8,e_w,v_w)
dis_0.9 <- prob(d_u_e,0.9,e_w,v_w)
dis_1   <- prob(d_u_e,1.0,e_w,v_w)
